The evolution of gene expression in the term placenta of viviparous mammals

### 2015-11-21 manuscript/manuscript.Rnw
discuss how go analysis was done properly

To determine enrichment levels of functional categories of genes in
highly-expressed transcripts in each transcriptome, we performed
functional annotation cluster analyses per transcriptome using DAVID
\cite{Huang.ea2009:Systematicandintegrativeanalysis,Sherman.ea2007:DAVIDKnowledgebasegene-centereddatabase}.
DAVID ranks functional annotation clusters according to enrichment
score (ES); functional annotation clusters are considered
significantly enriched if ES>1.3, as this corresponds to p<0.05
\cite{Huang.ea2009:Systematicandintegrativeanalysis}. We executed
analyses with two gene lists per transcriptome: 1) annotated genes
with expression levels of the top 5\% of the frequency distribution of
\ac{FPKM} and 2) the top 100 genes with the highest \ac{FPKM}. Due to the
paucity of annotated gene ontology terms for some species, gene lists
were compared using gene ontology terms derived from the human genome.

>>>>

To determine enrichment levels of functional categories of genes in
highly-expressed transcripts in each transcriptome, we performed
functional annotation cluster analyses per transcriptome using topGO
\cite{topGO:2.20.0}. Gene Ontology clusters were considered
significantly enriched if the \ac{FDR} as estimated by the Benjamini
and Hochberg procedure\cite{Benjamini1995:bh_procedure} on from the
$p$ values obtained from the Fisher Exact Test were less than or equal
to 0.05. Enrichment tests were considered with two gene lists per
transcriptome: annotated genes with expression levels of the top
5\% of the frequency distribution of \ac{FPKM} (Supplemental
\cref{tab:go_terms_enriched_top_five_dasypus_novemcinctus,tab:go_terms_enriched_top_five_equus_caballus,tab:go_terms_enriched_top_five_homo_sapiens,tab:go_terms_enriched_top_five_loxodonta_africana,tab:go_terms_enriched_top_five_monodelphis_domestica,tab:go_terms_enriched_top_five_mus_musculus,tab:go_terms_enriched_top_five_ovis_aries,tab:go_terms_enriched_top_five_pan_paniscus,tab:go_terms_enriched_top_five_sus_scrofa,tab:go_terms_enriched_top_five_ateles_fusciceps,tab:go_terms_enriched_top_five_nannospalax_galili,tab:go_terms_enriched_top_five_spalax_carmeli,tab:go_terms_enriched_top_five_bos_taurus,tab:go_terms_enriched_top_five_canis_familiaris});
the top 100 genes with the highest \ac{FPKM} (Supplemental
\cref{tab:go_terms_enriched_dasypus_novemcinctus,tab:go_terms_enriched_equus_caballus,tab:go_terms_enriched_homo_sapiens,tab:go_terms_enriched_loxodonta_africana,tab:go_terms_enriched_monodelphis_domestica,tab:go_terms_enriched_mus_musculus,tab:go_terms_enriched_ovis_aries,tab:go_terms_enriched_pan_paniscus,tab:go_terms_enriched_sus_scrofa,tab:go_terms_enriched_ateles_fusciceps,tab:go_terms_enriched_nannospalax_galili,tab:go_terms_enriched_spalax_carmeli,tab:go_terms_enriched_bos_taurus,tab:go_terms_enriched_canis_familiaris}).
Due to the paucity of annotated gene ontology terms for some species,
gene lists were compared using the \textit{Homo sapiens} Gene Ontology
using the 1:1 \textit{Homo sapiens} ortholog.
